### 2016-09-27 revision/introduction.tex
Reword one sentence in the intro

Finally, in Section~\ref{subsection:mirror-descent-lower-bound}, we show
negative results for existing popular variants of \textsc{MD}. We show two
examples that demonstrate that variants of \textsc{MD} can have $\Omega(T)$
regret (on sequences of loss vectors of unit norm) if the Bregman divergence
associated with the regularizer is unbounded. These results indicate that
\textsc{FTRL} is superior to \textsc{MD}.

>>>>

Finally, in Section~\ref{subsection:mirror-descent-lower-bound}, we show
negative results for existing popular variants of \textsc{MD}. We show two
examples of decision sets and sequences of loss vectors of unit norm on which
these variants of \textsc{MD} have $\Omega(T)$ regret.  These results indicate
that \textsc{FTRL} is superior to \textsc{MD}.
